Nail: A practical interface generator for binary formats

### 2014-04-01 paper/impl.tex
consistently use a non-breaking space (~) before \cite
rough intro pass done, with some sizable holes left

\section{Implementation}
The current prototype of the Nail parser generator supports the C programming language and top down parsers. Options for C++ STL data models and emitting Packrat parser
\cite{packrat-parsing:icfp02} are under heavy development. In this section, we will discuss some particular
features of our parser implementation.

>>>>

\section{Implementation}
\label{s:impl}

The current prototype of the Nail parser generator supports the C programming language and top down parsers. Options for C++ STL data models and emitting Packrat parser~\cite{packrat-parsing:icfp02} are under heavy development. In this section, we will discuss some particular
features of our parser implementation.

### 2014-04-01 paper/intro.tex
rough intro pass done, with some sizable holes left

Second, data formats can have constraints XXX todo.

@@

This paper presents the initial design and implementation of Nail, a
parser generator that greatly reduces the programmer effort required to
use a grammar-based parser.  Nail addresses the above three challenges
with several key ideas.  First, Nail XXX todo.

>>>>

Second, data formats can have constraints XXX todo.
Lengths.
Counts.
Checksums.

@@

This paper presents the initial design and implementation of Nail, a
parser generator that greatly reduces the programmer effort required to
use a grammar-based parser.  Nail addresses the above three challenges
with several key ideas.  First, Nail XXX todo.  Bijections.  Reduced
expressiveness.  Constraints.  External interaction (checksum, ports,
etc).

We have implemented an initial prototype of Nail in C\@.  Our experience
so far suggests that it is a promising approach: we were able to construct
a succinct grammar for DNS packets, and write a small DNS server that
uses Nail for all packet input and output, and operates purely on
Nail-generated data structures, with no need for any semantic actions.

The rest of this paper is organized as follows.  \S\ref{s:relwk}
puts Nail in the context of related work.  \S\ref{s:design} describes
Nail's design.  \S\ref{s:impl} discusses our initial implementation
of Nail.  \S\ref{s:eval} provides some initial evaluation results.
\S\ref{s:future} suggests several directions for future work, and
\S\ref{s:concl} concludes.
